SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/paper.tex
removed inappropriate comma

SciPy has provided special functions and leveraged BLAS and
LAPACK\cite{LAPACK} routines for many years. SciPy now additionally
includes Cython\cite{behnel2011cython} wrappers for
many BLAS and LAPACK routines (added in 2015), and the special functions 
provided in the \texttt{scipy.{\allowbreak}special} submodule (added in 2016).  
These Cython wrappers are available in the modules
\texttt{scipy.{\allowbreak}linalg.{\allowbreak}cython\_blas},
\texttt{scipy.{\allowbreak}linalg.{\allowbreak}cython\_lapack}, and
\texttt{scipy.{\allowbreak}special.{\allowbreak}cython\_special} respectively.
When writing algorithms in Cython, it is typically more efficient to call
directly into the libraries SciPy wraps rather than indirectly, using SciPy's
Python APIs.  These low-level interfaces for Cython can also be used outside of
the SciPy codebase to gain access to the functions in the wrapped libraries
while avoiding the overhead of Python function calls.  This can give
performance gains of one or two orders of magnitude for many use cases.

>>>>

SciPy has provided special functions and leveraged BLAS and
LAPACK\cite{LAPACK} routines for many years. SciPy now additionally
includes Cython\cite{behnel2011cython} wrappers for
many BLAS and LAPACK routines (added in 2015) and the special functions 
provided in the \texttt{scipy.{\allowbreak}special} submodule (added in 2016).  
These Cython wrappers are available in the modules
\texttt{scipy.{\allowbreak}linalg.{\allowbreak}cython\_blas},
\texttt{scipy.{\allowbreak}linalg.{\allowbreak}cython\_lapack}, and
\texttt{scipy.{\allowbreak}special.{\allowbreak}cython\_special} respectively.
When writing algorithms in Cython, it is typically more efficient to call
directly into the libraries SciPy wraps rather than indirectly, using SciPy's
Python APIs.  These low-level interfaces for Cython can also be used outside of
the SciPy codebase to gain access to the functions in the wrapped libraries
while avoiding the overhead of Python function calls.  This can give
performance gains of one or two orders of magnitude for many use cases.
